---
title: "<hw4_p8105_wz2722"
author: "wentao zhou"
date: "2024-10-30"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

```{r}
library(distill)
create_website(dir = "my-website", title = "My Website")


```


# This is Wentao's  website
git clone https://github.com/Wentao-Zhou/hw4_p8105_wz2722.git

 

Q2.Create a flexdashboard

Here’s the code to create a flexdashboard with plotly using the NY NOAA dataset from the p8105.datasets package. This dashboard includes a scatter plot, a line plot, and a bar plot. You can filter or sample the data to improve performance.


---
title: "NY NOAA Weather Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
# Load necessary libraries
library(flexdashboard)
library(plotly)
library(dplyr)
library(lubridate)
library(p8105.datasets)

# Load the NY NOAA dataset and filter
data("ny_noaa")

# Filter and sample the data for reasonable performance
set.seed(42)
ny_noaa_sample <- ny_noaa %>%
  filter(!is.na(tmax), !is.na(tmin), !is.na(prcp)) %>%
  mutate(date = ymd(date),
         year = year(date)) %>%
  sample_n(5000)
```


Temperature Over Time (Scatter Plot)


```{r}
# Scatter plot: Maximum temperature over time
plot_ly(ny_noaa_sample, 
        x = ~date, 
        y = ~tmax, 
        type = 'scatter', 
        mode = 'markers',
        marker = list(color = 'red', size = 5)) %>%
  layout(title = "Maximum Temperature Over Time",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Max Temperature (°C)"))

```


Average Temperature by Year (Line Plot)
```{r}
# Ensure tmax and tmin are numeric
ny_noaa_sample <- ny_noaa_sample %>%
  mutate(tmax = as.numeric(tmax),
         tmin = as.numeric(tmin))

# Line plot: Average temperature by year
avg_temp_by_year <- ny_noaa_sample %>%
  group_by(year) %>%
  summarize(avg_temp = mean((tmax + tmin) / 2, na.rm = TRUE))

# Plot the line plot
plot_ly(avg_temp_by_year, 
        x = ~year, 
        y = ~avg_temp, 
        type = 'scatter', 
        mode = 'lines+markers') %>%
  layout(title = "Average Temperature by Year",
         xaxis = list(title = "Year"),
         yaxis = list(title = "Average Temperature (°C)"))

```

Precipitation by Year (Bar Plot)

```{r}
# Bar plot: Total precipitation by year
total_precip_by_year <- ny_noaa_sample %>%
  group_by(year) %>%
  summarize(total_precip = sum(prcp, na.rm = TRUE))

plot_ly(total_precip_by_year, 
        x = ~year, 
        y = ~total_precip, 
        type = 'bar',
        marker = list(color = 'blue')) %>%
  layout(title = "Total Precipitation by Year",
         xaxis = list(title = "Year"),
         yaxis = list(title = "Total Precipitation (mm)"))

```
Code Explanation
Scatter Plot: Visualizes maximum temperature over time.
Line Plot: Shows the yearly average temperature.
Bar Plot: Displays total precipitation for each year.

